Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-11-19 paper/ms.tex
More wordsmithing on Carlyn's paper.

\begin{abstract}
Recent studies of stellar evolution predict the existence of "hybrid" white 
dwarfs, made of a C/O/Ne
core within a O/Ne shell, and that these are viable progenitors for supernovae.
More recent work found that the C/O core is mixed with the surrounding O/Ne
while the WD cools. Inspired by this scenario, we performed simulations of
thermonuclear supernovae from these hybrid progenitors. The progenitor model 
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing 
followed by accretion until it reached conditions for the ignition of 
carbon burning. The MESA model was then mapped to a two-dimensional initial 
condition and an explosion simulated with FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
WD. By comparing the yields of the explosions, we found....
how explosions from these models differ from explosions from previous models
without the mixing during the WD cooling.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.5 \Msun of material composed principally 
of C and O burns under degenerate conditions. This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}.

Supernovae are observationally classified 
by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios, the {\em double detonation} or {\em sub-Chandrasekhar}
scenario, the {\em white dwarf merger} scenario, and  
the {\em single degenerate} scenario.

When a main sequence star runs out of fuel, it dies off to become a dense
remnant of the MS, known as a white dwarf. Type Ia Supernova are bright
explosions produced from radioactive Ni-56 determined by the white dwarf
(WD). Astronomers use the fact that they give off a known amount of light
and the inverse square law to determine distances of far objects. They
were also used to find Hubble’s expansion of the universe.

@@

\subsection{The Chandrasekhar-mass Single Degenerate Scenario}

>>>>

\begin{abstract}
Recent studies of stellar evolution predict the existence of "hybrid" white 
dwarfs, made of a C/O/Ne
core within a O/Ne shell, and that these are viable progenitors for supernovae.
More recent work found that the C/O core is mixed with the surrounding O/Ne
while the white dwarf cools. Inspired by this scenario, we performed simulations of
thermonuclear supernovae from these hybrid progenitors. The progenitor model 
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing 
followed by accretion until it reached conditions for the ignition of 
carbon burning. The MESA model was then mapped to a two-dimensional initial 
condition and an explosion simulated with FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
white dwarf. By comparing the yields of the explosions, we found....
how explosions from these models differ from explosions from previous models
without the mixing during the white dwarf cooling.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.5 \Msun of material composed principally 
of C and O burns under degenerate conditions. This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}. 
This special property of the light curve is thought to follow
from the fact that the source of luminosity, the radioactive decay
of \Ni{56}, synthesized by the thermonuclear burning, is also the
principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.

Supernovae are classified observationally 
by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
~0.6 CHECK THIS \Msun needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star. Within this
progenitor setting, the models that best reproduce the observed
stratified ejecta are those in which the burning begins as a 
subsonic deflagration, which allows the star to react and expand
thus lowering the density, that is followed by a 
detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
We adopt this setting for the explosion simulations we present and 
describe our approach in detail below.

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.

. This scenario 
provides an abundance of degenerate fuel, which may explain some 
The other main class of models is the DD progenitor,
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
This scenario includes inspiraling pairs, collisions, violent mergers,
and also the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

@@

\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
